---
title: "Research Question"
format: html
editor: visual
---

Step 1. Install necessary packages.

```{r}
install.packages("tidyverse")
install.packages("kableExtra")
```

Step 2. Declare that you will use these packages in this session.

```{r}
library("tidyverse")
library("kableExtra")
```

Step 3. Upload the dataframe that you have created in Spring 2024 into the repository.

Step 4. Open the dataframe into the RStudio Environment.

```{r}
df<-read.csv("data.csv")
```

Step 5. Use the **head** and **kable** function showcase the first 10 rows of the dataframe to the reader.

```{r}
kable(head(df))
```

## Question 1: What is the frequency of this data frame?

Answer:

## Question 2: What is the cross-sectional (geographical) unit of this data frame?

Answer:

Step 6. Use the **names** function to display all the variables (column) in the dataframe.

```{r}
names(df)
```

## Question 3: Which column represents the explanatory variable of interest?

Answer:

## Question 4: Which column represents the outcome variable of interest?

Answer:

Step 7: Fit a regression model $y=\beta_0 + \beta_1 x + \epsilon$ where $y$ is the outcome variable and $x$ is the treatment variable. Use the **summary** function to display the results.

```{r}
model1<-lm(nox_emit ~ nbp, data=df)

summary(model1)
```

Step 9: Change the document format to gfm

Step 10: Render the document

Step 11: Push the document back to GitHub and observe your beautiful document in your repository!

Step 12: If your team has a complete dataframe that includes both the treated and outcome variable, you are done with the assignment. If not, make a research plan in Notion to collect data on the outcome and treatment variable and combine it into one dataframe.
