---
title: "
Q1: How can we best predict each firm’s lobbying spending on the Waxman-Markey bill?
Q2: How do certain characteristics of a company predict how much money they'll spend on lobbying for the Waxman-Markey bill?
"
format: gfm
editor: visual
---

## Data Description

Step 1. Install necessary packages.

```{r}
install.packages("tidyverse")
install.packages("kableExtra")
```

Step 2. Declare that you will use these packages in this session.

```{r}
library("tidyverse")
library("kableExtra")
```

Step 3. Upload the dataframe that you have created in Spring 2024 into the repository.

Step 4. Open the dataframe into the RStudio Environment.

```{r}
df<-read.csv("finaldatasets/4. merge with meng/merged_meng.csv")
```

Step 5. Use the **head** and **kable** function showcase the first 10 rows of the dataframe to the reader.

```{r}
kable(head(df))
```

## Question 1: What is the frequency of this data frame?

Answer: 0, data tacken during the waxman markey bill period

## Question 2: What is the cross-sectional (geographical) unit of this data frame?

Answer: Company

Step 6. Use the **names** function to display all the variables (column) in the dataframe.

```{r}
names(df)
```

## Question 3: Which column represents the explanatory variable of interest?

Answer: Total.GHG and NAICS

## Question 4: Which column represents the outcome variable of interest?

Answer: lobby_amount

Step 7: Fit a regression model $y=\beta_0 + \beta_1 x + \epsilon$ where $y$ is the outcome variable and $x$ is the treatment variable. Use the **summary** function to display the results.

```{r}
table(df$NAICS)
model1<-lm(lobby_amount ~ Total.GHG + as.factor(NAICS), data=df)

summary(model1)
```

## Question 5: What is the equation that describes the linear regression above? Please include an explanation of the variables and subscripts.

$$
lobby_i = \beta_0 + \beta_1 \times Total.GHG_i + \beta_2 \times \delta_{NAIC} +  \epsilon_i
$$

where $i$ represents each company

## Question 6: What fixed effects can be included in the regression? What does each fixed effects control for? Please include a new equation that incorporates the fixed effects.

We already included a fixed effect which was a dummie variable for NAICS336411 after finding it to be the only significant NAICS sector predictor.

## Question 7: Run a new regression with the fixed effects. Does the RMSE improve?

Step 9: Change the document format to gfm

Step 10: Change the filename to README.qmd. Render the document

Step 11: Push the document back to GitHub and observe your beautiful document in your repository!
